Movie Recommendation System

### 2021-03-23 Sherbourne_Capstone.Rmd
Capstone

From the website/readme file, the data is described as just over 10 million ratings from users who rated at least 20 movies each. Users are only represented by their a unique and anonymized id number. Ratings were made on a scale from 0.5 stars (worst) to 5 stars (best) in increments of 0.5. The timestamp variable represents seconds form midnight UTC of January 1, 1970. The genres variable contains a combinations of 18 possible genres. Looking at the first few lines of data, there are a few data munging operations that will help with further processing:

@@

@@

The following bar chart shows the number frequency of movie genres. Drama and Comedy stand out as the biggest genres. 
```{r, echo=FALSE}
(genre_count <-edx %>% distinct(edx$movieId, .keep_all = TRUE) %>% select(9:26) %>% 
    colSums()) %>% barplot(las=2, main = 'Movie Genres', ylab = 'Count')
```

@@

```{r, echo=FALSE, message=FALSE}
(final_rmse <- RMSE(final_prediction, validation$rating))
```

>>>>

From the website/readme file, the data is described as just over 10 million ratings from users who rated at least 20 movies each. Users are only represented by their a unique and anonymized id number. Ratings were made on a scale from 0.5 stars (worst) to 5 stars (best) in increments of 0.5. The timestamp variable represents seconds form midnight UTC of January 1, 1970. The genres variable contains a combinations of 18 possible genres. Below is a look at the first few lines of data:

@@

There are a few data munging operations that will help with further processing:

@@

The following bar chart shows the number of movie genres. Drama and Comedy stand out as the biggest genres. 
```{r, echo=FALSE}
(genre_count <-edx %>% distinct(edx$movieId, .keep_all = TRUE) %>% select(9:26) %>% 
    colSums()) %>% barplot(las=2, main = 'Movie Genres', ylab = 'Count')
```

@@

```{r, echo=FALSE, message=FALSE}
final_rmse <- RMSE(final_prediction, validation$rating)
cat('Final RMSE: ', final_rmse)
```
